\LARGE \bf Steering a Swarm Using Global Inputs And Swarm Statistics

### 2016-08-05 journalSwarmControl/realExperiment.tex
Added Pics

The kilobots performed five successful runs of object manipulation through the obstacle maze.
Each trial used 100 kilobots. Videos of each are in the multimedia extension. Trials 2-5 were performed in a row with no failures in between.  For each trial, fully charged kilobots were placed in the lower left-hand of the workspace, as shown in Fig.~\ref{fig:expSnapShot}.  The moveable object was placed in the lower center of the workspace.  The same controller as in the simulation, Alg.~{alg:BlockPushing}, but with discretized control inputs, was coded in {\sc Matlab}.  Trials were run until the object COM entered the goal region.  The trials ran for \{ \todo{123123,12312,12312,12321,123123} \} (minutes:seconds).  This is a mean of \todo{34} and a standard deviation of \todo{234}.

>>>>

The kilobots performed five successful runs of object manipulation through the obstacle maze.
Each trial used 100 kilobots. Videos of each are in the multimedia extension. Trials 2-5 were performed in a row with no failures in between.  For each trial, fully charged kilobots were placed in the lower left-hand of the workspace, as shown in Fig.~\ref{fig:expSnapShot}.  The moveable object was placed in the lower center of the workspace.  The same controller as in the simulation, Alg.~{alg:BlockPushing}, but with discretized control inputs, was coded in {\sc Matlab}.  Trials were run until the object COM entered the goal region.  The trials ran for \{ 24:25, 57:37, 50:00, 36:02, 45:07\} (minutes:seconds).  This is a mean of \{42:38\} (minutes:seconds) and a standard deviation of \{234\}.
